On centrality of orthogonal $\Kt$

### 2016-04-22 paper.tex
Minor

\section{Principal notation}

@@

In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections 
$$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$
where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit. The Steinberg group is a group given by formal generators
$$\{x_{ij}(r)\mid1\leq i\neq j\leq n,\ r\in R\}$$
and Steinberg relations
\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\begin{align}
&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s),\\
&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i,\\
&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs).
\end{align}
All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. 
Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.

>>>>

\section{Principal notation}
In the present paper $R$ denotes commutative (associative, unital) ring, $l\geq3$, and $n=l+1\geq4$, $R^n$ is a free (right) $R$-module with basis $e_1,\ldots,e_n$, 
$\GL(n,\,R)$ is a group of invertible $n\times n$ matrices over $R$, $\E(n,\,R)$ its elementary subgroup generated by elementary transvections

@@

$$\{t_{ij}(r)=1+e_{ij}r\mid1\leq i\neq j\leq n,\ r\in R\},$$
where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit. The Steinberg group is a group given by formal generators
$$\{x_{ij}(r)\mid1\leq i\neq j\leq n,\ r\in R\}$$
and Steinberg relations
\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\begin{align}
&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s),\\
&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i,\\
&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs).
\end{align}
All commutators in the present paper are left-normed, $[x,\,y]=xyx\inv y\inv$. 
Denote $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ a natural projection sending $x_{ij}(r)$ to $t_{ij}(r)$.
